### 2021-09-07 man-roxygen/seeds.Rmd
update wording with Mine's suggestion

When using the infer package for research, or in other cases when exact reproducibility is a priority, be sure the set the seed for R's random number generator. infer will respect the random seed specified in the `set.seed()` function, returning the same results when `generate()`ing new data given an identical seed. For instance, we can calculate the difference in mean `age` by `college` degree status using the `gss` dataset from 10 versions of the `gss` resampled with permutation using the following code.

@@

Setting the seed again and rerunning the same code will result in the same answer.

>>>>

When using the infer package for research, or in other cases when exact reproducibility is a priority, be sure the set the seed for R's random number generator. infer will respect the random seed specified in the `set.seed()` function, returning the same result when `generate()`ing data given an identical seed. For instance, we can calculate the difference in mean `age` by `college` degree status using the `gss` dataset from 10 versions of the `gss` resampled with permutation using the following code.

@@

Setting the seed to the same value again and rerunning the same code will produce the same result.
